---
title: "Fetching / Loading Data"
author: "Justin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fetch data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}


First, setup by loading the package and setting working directory
```{r, eval=TRUE, results='asis'}
library(devtools)
outputdir = "."
path_to_Rpkg_directory = "."
setwd(path_to_Rpkg_directory)
load_all()
```

Here is an example. Let us try to fetch national influenza intensity measurements (called `weighted ILI', or `wILI' for short), from the [link](fluview) interface using the function `fetchEpidataDF()`:
```{r, eval=TRUE, results='markup'}
fluview.nat.all.df = fetchEpidataDF(source = "fluview", 
                                    area   = "nat",
                                    first.week.of.season=21L)
## See first few lines
head(fluview.nat.all.df,3)
tail(fluview.nat.all.df,3)
```
	
What if we wanted to fetch Google flutrends (GFT) measurements using the same function, under the same date range and settings?
```{r, eval=TRUE, results='asis'}
gft.nat.all.df = fetchEpidataDF(source = "gft", 
                                    area   = "nat",
                                    first.week.of.season=21L)
```
Note, GFT measurements are 1/100'th the scale of wILI measurements.

There are also 10 sub-regions of the united states (see [link](here) for more) whose influenza intensity measurements are available; they can be queried as follows:
```{r,  eval=TRUE, results='asis'}
gft.reg.dat = fetchEpidataDF(source = "gft", 
                             area ="hhs1")
fluview.reg.dat = fetchEpidataDF(source = "fluview", 
                             area ="hhs1")
```

How would you query data from a certain date ranges, but from two or more sources? Use the wrapper `fetchEpidataDF.multiple.sources()`
```{r, eval=TRUE}
all.reg.dat = fetchEpidataDF.multiple.sources(source = c("gft, hhs1"), area = "hhs1")
```

