---
title: "Making forecasts with basis regression"
author: "Justin"
date: "`r Sys.Date()`"
head-includes:
- \usepackage{bbm}
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Making forecast with BR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---
First, setup by loading the package and setting working directory
```{r, eval=TRUE, results='asis'}
library(devtools)
outputdir = "."
path_to_Rpkg_directory = "."
setwd(path_to_Rpkg_directory)
load_all()
```

Let us first fetch national influenza intensity measurements (called `weighted ILI', or `wILI' for short), from the [link](fluview) interface using the function `fetchEpidataDF()`:
```{r, eval=TRUE, results='markup'}
## Bare minimum
fluview.nat.df = fetchEpidataDF(source = "fluview", 
                                area   = "nat",
                                first.week.of.season=21L)

## And with some more options
area.name = "nat"
fluview.nat.df = fetchEpidataFullDat(source = "fluview", area = "nat",
                                     signal.ind = "wili",
                                     min.points.in.season = 52L,
                                     first.week.of.season = 21L,
                                     cache.file = sprintf("fluview_%s_fetch.Rdata", area.name))
```
A short explanation: Use `wili` for `source=fluview` option, `gft` for the `source=gft` option. `min.points.in.season` should be 52 if you are at forecasting time, and you would like to only take the fully observed historical seasons. The seemingly peculiar choice of `first.week.of.season=21` is a detail in the modeling and implementation of BR (and other methods, too!) that comes from that fact that the 21'st _calendar_ week in any given year is a convenient customary cutoff for which the trajectory of flu intensity measurements, when plotted, seem to be centered (on average).

See the vignette [link](fetch_data.Rmd) for more details about fetching data.

Let's focus our attention on the 'hhs1' region:
```{r, eval=TRUE, results='markup'}
area.name = "hhs1"
full.dat = fetchEpidataFullDat("fluview", area.name, "wili",
                               min.points.in.season=52L,
                               first.week.of.season = 21L,
                               cache.file=sprintf("fluview_%s_fetch.Rdata", area.name))
```

The default settings of BR is straightforward to use
```{r, eval=TRUE, results='markup'}
# Try BR with basic options
mysim = br.sim(full.dat, max.n.sims=1000)
plot(mysim) 
print(mysim)
targets = target_forecast(mysim, "pht")
print(targets)
```